%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------
\cventry
{Senior Software Engineer} % Job title
{LiAuto} % Organization
{Shenzhen, China} % Location
{Jan. 2024 -} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Street layout and dynamic objects reconstruction in urban areas for autonomous simulation}
\item {Controllable vehicles manipulation in reconstructed scenes}
\end{cvitems}
}

\cventry
{Chief Software Engineer} % Job title
{Huawei Riemann Lab} % Organization
{Shenzhen, China} % Location
{Dec. 2022 - Dec. 2023} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {3D geometric reconstruction in city-scale towards urban area and complex facilities}
\end{cvitems}
}

\cventry
{Research Intern} % Job title
{Synthesia} % Organization
{London, UK} % Location
{Jun. 2022 - Oct. 2022} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {High-fidelity Neural Actor}
\end{cvitems}
}

\cventry
{Research Intern} % Job title
{Facebook Reality Lab \textit{Research}} % Organization
{Seattle, USA} % Location
{Jun. 2021 - Oct. 2021} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Single-view semantic 3D eye reconstruction for eye tracking}
\end{cvitems}
}
%------------------------------------------------

\cventry
{Prize Winner} % Job title
{Microsoft Research} % Organization
{Redmond, USA} % Location
{Apr. 2016 - May 2016} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Make multi-thread deep learning for CNTK, awarded as global 2$^\text{nd}$ prize in \href{https://www.microsoft.com/en-us/research/academic-program/microsoft-open-source-challenge/}{\color{awesome-skyblue}{\underline{Microsoft open source challenge}}}.} % Title
\end{cvitems}
}

\cventry
{Software Engineer} % Job title
{OpenCV -- sponsored by Google} % Organization
{Beijing, PRC} % Location
{Apr. 2015 - Sep. 2016} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {An initial developer of \href{https://github.com/tiny-dnn/tiny-dnn}{\color{awesome-skyblue}{\underline{tiny-dnn}}}, which is the deep learning backend for OpenCV}.
\item {Contributed 3 OpenCV modules: \href{https://www.youtube.com/watch?v=Mc20rTYdXTE}{\color{awesome-skyblue}{\underline{3D multi-task learning}}}, \href{https://summerofcode.withgoogle.com/archive/2016/projects/4623962327744512}{\color{awesome-skyblue}{\underline{quantized deep learning}}} and \href{https://summerofcode.withgoogle.com/archive/2019/projects/6247164785721344}{\color{awesome-skyblue}\underline{super resolution}}.}
\end{cvitems}
}

%------------------------------------------------

\end{cventries}
